---
title: "My Storyboard at DACSS - tabs"

output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
```

## Sidebar {.sidebar}


Preparing the dashboard based on the instructions given at @magallanes_reyes_data_2022, and @aden-buie_flexdashboard_2023.

## Column {.tabset .tabset-fade}


### Histogram Of Cout of companies under each industry

```{r}
readRDS("draft1.rds")
```


### Percentage of Unemployment By Country

```{r}
readRDS("Plot2.rds")
```

### Box Plot of Precentage of Layoff By Industry

```{r}
readRDS("Plot3.rds")
```


### Bi Variate Plot - Relationship between Company Size and Money Raised(Before Layoff)

```{r}
readRDS("Plot4.rds")
```


### Multi Variate Plot - Relation between company size and money raised (After layoff) 

```{r}
readRDS("Plot5.rds")
```


### Map Plot of Layoffs of companies by Industry

```{r}
readRDS("Plot6.rds")
```


### Map Plot concerning money rasied in Mil by companies in Asia

```{r}
readRDS("Plot7.rds")
```


### References : 

